Improving Code Completion in Pharo\\Using N-gram Language Models

### 2020-02-19 ACM/abstract.tex
added a footnote about pharo
finalised the abstract

\begin{abstract}
In this paper we present applying statistical language models to improve code completion
in Pharo. In particular, the goal is to use n-gram models for sorting the completion
candidates and in such a way increase the relevancy of untyped suggestions.

\section{Introduction}
\oz{Ask Stephane if you should add an affiliation with Inria and RMoD}
Code completion is one of the essential features of any IDE that greatly improves the
developer experience. Thus, it is important to find a way to make it as effective as
possible. Specifically, in the case of Pharo, a dynamically-typed programming language
and IDE, in the last year and a half a lot of work has been carried out to improve code
completion. However, there are more potential improvements from which developers can only
benefit, such as improving the relevance of suggestions and hence reducing time and
effort the developer spends to go through the list of completions.

@@

\section{Conclusion}
In this paper we proposed applying n-gram language models when sorting completion candidates
in Pharo. Having an AST-based completion engine, we are not always able to infer type information
from the nodes, and hope to compensate for it and improve the relevance of suggestions by
implementing a fast n-gram based sorting to be used in the Pharo IDE.

>>>>

\begin{abstract}
In this paper we present applying statistical language models to improve code completion
in Pharo \footnote{https://pharo.org/}. In particular, the goal is to use n-gram models for
sorting the completion candidates and in such a way increase the relevancy of untyped suggestions.

\section{Introduction}
Code completion is one of the essential features of any IDE that greatly improves the
developer experience and productivity. Thus, it is important to find a way to make it as effective as
possible. Specifically, in the case of Pharo, a dynamically-typed Smalltalk-based programming language
and IDE, in the last year and a half a lot of work has been carried out to improve code
completion. However, there are more potential improvements from which developers can only
benefit, such as improving the relevance of suggestions and hence reducing time and
effort the developer spends to go through the list of completions.

@@

\section{Conclusion}
In this paper we proposed applying n-gram language models when sorting completion candidates
in Pharo. Having an AST-based completion engine, we are not always able to infer type information
from the nodes, and hope to compensate for it and improve the relevance of suggestions by
implementing a fast n-gram based sorting functionality to be used in the Pharo IDE.
